% Do not chage this part
\begin{center}
  \textbf{{\Large ACKNOWLEDGEMENT}}\\[60pt]
\end{center}
\addcontentsline{toc}{chapter}{\textbf{\normalsize{\emph{ACKNOWLEDGEMENT}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The text herein are only samples, change them to your taste
First of all I would like to thank my supervisor, Dr. Md. Monirul Islam for introducing me to the amazingly interesting world of Machine Learning and Data Analysis. And he is the very first person who taught me how to perform research work efficiently. Without him and his continuous supervision, guidance and valuable advice, it would have been impossible for me to come at this point and have some output from the thesis. I am specially grateful to him for allowing me greater freedom in choosing the problems to work on, for his encouragement at times of disappointment, and for his patience with my wildly sporadic work habits.

I would also want to thank my fellow friends Md. Thohidul Islam, Shariful Islam Foysal and Md. Moyeen Uddin Fahim for their encouragement, insightful comments, and hard questions. They gave their best support to complete my thesis timely.
I would like to express my gratitude to all our teachers. Their motivation and encouragement in addition to the education they provided meant a lot to me.

Last but not the least, I would like to thank my family, my parents, for giving birth to me at the first place and supporting me spiritually throughout my life.

\vspace*{20.0mm}

\begin{minipage}[t]{0.2\textwidth}
  Dhaka\par
  \thesisdate
\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\textwidth}
  \begin{enumerate}
    \vspace{-0.75\baselineskip}
    \DTLforeach{ThesisStudents}{\StudentName=Column1}{\item[]\StudentName}
  \end{enumerate}
\end{minipage}

\endinput
